
\documentclass[a4paper,fleqn]{cas-sc}

\usepackage[authoryear,longnamesfirst]{natbib}


%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
%%%

\input{./newcommands}
\usepackage{graphicx} 

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

% Short title
\shorttitle{Cloud-based Image Processing}    

% Main title of the paper
\title [mode = title]{On the Use of Reference Nets for Building Cloud-based Scientific Workflows}  

% Title footnote mark
% eg: \tnotemark[1]
%\tnotemark[<tnote number>] 

% Title footnote 1.
% eg: \tnotetext[1]{Title footnote text}
%\tnotetext[<tnote number>]{<tnote text>} 

% First author
%
% Options: Use if required
% eg: \author[1,3]{Author Name}[type=editor,
%       style=chinese,
%       auid=000,
%       bioid=1,
%       prefix=Sir,
%       orcid=0000-0000-0000-0000,
%       facebook=<facebook id>,
%       twitter=<twitter id>,
%       linkedin=<linkedin id>,
%       gplus=<gplus id>]

%\author[1]{Hayat Bendoukha}[]

% Corresponding author indication
%\cormark[<corr mark no>]

% Footnote of the first author
%\fnmark[<footnote mark no>]

% Email id of the first author
%\ead{hayat.bendoukha@univ-usto.dz}

% URL of the first author
%\ead[url]{<URL>}

% Credit authorship
% eg: \credit{Conceptualization of this study, Methodology, Software}
%\credit{<Credit authorship details>}

% Address/affiliation
%\affiliation[1]{organization={Département d'Informatique, Faculté des Mathématiques et Informatique, Université des Sciences et de la Technologie d'Oran %Mohamed  Boudiaf},
%            addressline={BP 1505, El Mnaouer}, 
%            city={Oran},
%          citysep={}, % Uncomment if no comma needed between city and postcode
%            postcode={31000}, 
%            state={},
%            country={Algeria}}

% Corresponding author text
%\cortext[1]{Corresponding author}

% Footnote text
%\fntext[1]{}

% For a title note without a number/mark
%\nonumnote{}


% Here goes the abstract
\begin{abstract}
Cloud computing provides scientists with a large number of powerful resources.
%
These resources enhance the productivity of the whole system.
%
Running complex scientific workflows on Cloud resources rather then on-premise increases the performance of execution.
%
Nevertheless, traditional scientific workflow management systems (SWfM) are not yet adapted for the Cloud.
%
Creating scientific workflows and executing them in the Cloud still face many challenges due to the complexity of the Cloud environment. 
%
Besides, migrating a part or the whole scientific application to the Cloud is not trivial.
%
It should be based on a solid strategy.
%
Issues like: Where to store the data and where to execute the processes need to be investigated.
%
In this paper, we first present \RenewGrass{}, a tool for modeling and executing image processing workflows by \emph{reference nets}.
%
Then, we discuss the deployment of \RenewGrass{} into the Cloud.
%
This work includes also a use case example related to the remote sensing domain.
%

\end{abstract}


% Keywords
% Each keyword is seperated by \sep
\begin{keywords}
Workflows \sep RenewGrass \sep Petri Nets \sep Cloud computing \sep Image processing 
\end{keywords}

\maketitle

\section{Introduction}
\input{introduction}

\section{Related Work and Background}
\input{functionality}

\section{\RenewGrass{}}
\input{grassintegration}

\section{\RenewGrass{} in the Cloud}
\input{cloudmigration}

\section{Discussion}
\input{discussion}

\section{Conclusion}
\input{conclusion}



%% Loading bibliography style file
\bibliographystyle{cas-model2-names}

% Loading bibliography database
\bibliography{main}

% Biography
\bio{}
% Here goes the biography details.
\endbio

%\bio{pic1}
% Here goes the biography details.
\endbio

\end{document}


